---
title: "p8105_hw5_cw3555"
author: "Eunice Wang"
date: "2023-11-15"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.

```{r}
library(tidyverse)
library(rvest)
```

Set seed for reproducibility.

```{r}
set.seed(12345)
```


### Problem 1

#### Load and describe the raw data.

```{r}
homicide_data=
  read_csv("data/homicide-data.csv") |> 
  janitor::clean_names()

homicide_data
```

The raw data contains `r nrow(homicide_data)` obervations (homicide cases) of `r ncol(homicide_data)` variables(including the date, location of each case,whether an arrest was made and basic demographic characteristics of the victim). It reported homicides in 50 large U.S. cities.

#### Create a city_state variable and then summarize.

```{r}
city_summary=
  homicide_data |> 
  mutate(city_state=str_c(city,state,sep =", ")) |> 
  group_by(city_state) |> 
  summarize(
    total_homicides=n(),
    unsolved_homicides=sum(disposition %in% c("Closed without arrest","Open/No arrest"))
    )
```

#### For Baltimore, MD

Estimate the proportion of homicides that are unsolved.
```{r}
baltimore_df=
  city_summary |> 
  filter(city_state=="Baltimore, MD") 

baltimore_prop_test=
  prop.test(
    x=pull(baltimore_df, unsolved_homicides),
    n=pull(baltimore_df, total_homicides)
  )
```

Save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_tidied=
  broom::tidy(baltimore_prop_test)

baltimore_output=
  baltimore_tidied |> 
  select(estimate,conf.low, conf.high)
```
* The estimated proportion of unsolved homicides in Baltimore is `r pull(baltimore_tidied, estimate) |> round(3)`, and the confidence interval is (`r pull(baltimore_tidied, conf.low) |> round(3)`,`r pull(baltimore_tidied, conf.high)|> round(3)`)

#### For each cities

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
city_output=
  city_summary |> 
  mutate(
    prop_test_output = 
      map2(
        unsolved_homicides,
        total_homicides,
        ~prop.test(x=.x,n=.y)
      ) 
  ) |> 
  mutate(tidied_output= map(prop_test_output, broom::tidy)) |> 
  unnest(tidied_output) |> 
  select(city_state,estimate,conf.low, conf.high)

head(city_output)
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides

```{r}
city_output |> 
  ggplot(aes(x=reorder(city_state,-estimate), y=estimate))+
  geom_point()+
  geom_errorbar(
    aes(
      ymin= conf.low,
      ymax= conf.high),
      width=0.2)+
  coord_flip()+
  labs(
    title= "Proportion of Unsolved Homicides by City",
    x="City",
    y="Estimated Proportion of Unsolved Homicides")+
  theme_minimal()
```

We can see Chicago is the city with most unsolved homicides, whole Tulsa is the city with fewest unsolved homicides.




